Irt plot extra

### 2022-03-29 manuscript.Rmd
Spell-check 3

**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the educational grade level required to understand the items in our tool using Flesch-Kincaid grade level identification method [@flesch1948new]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.

**Lastly**, we developed a short form of LEBA using Item Response Theory (IRT) based analysis. We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`). IRT assesses the item quality by estimating item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017]. Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$). Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%. Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017]. We discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA. We also assessed the precision of the short LEBA using Test information curve (TIC). TIC indicates the amount of information a particular scale carries along the latent trait continuum. Item fit and person fit of the fitted IRT models were also analysed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018]. Item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit. Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].

@@

### Exploratory Factor Analysis

@@

### Confirmatory Factor Analysis and Reliability Analysis

@@

png(filename="Figures/CFAplot2.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=12, 
    pointsize=12, 
    res=1200)
semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20). We discarded those items which yielded a short form of LEBA with 5 factors and 18 items.

@@

We treated each factor of short-LEBA as a unidimensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)). These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$). The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].

@@

Though there are lots of validated tool to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure. At present there is a dearth of validated tool to measure light exposure related behaviours. In that vein we have developed a subjective self-reported tool that can capture light exposure related behaviour in different dimensions.

@@

We developed a novel self-reported subjective tool-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour. We developed 48 items, judged the relevance and content of the items and conducted a large scale geographically unrestricted cross-sectional survey. Our EFA gave a five solution with 25 items. A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded. The 23-item "LEBA" was found reliable (internal consistency) and valid (structural validity). A short-form of LEBA was developed using IRT analysis. IRT analysis gave a 18-item scale with a good coverage across the underlying trait continuum. Hence, we could recommend that LEBA can be used to measure different aspects of light exposure related behaviour.

@@

Since, LEBA is the first of its kind, estimating convergent validity with other subjective tool was not possible. One way to establish the convergent validity of LEBA is to administer this subjective tool along which some objective measurement tools (e.g. personalised light dosimeter). Though such objective tools do not directly capture light exposure related behaviour, potential insight can be drawn by understanding the behaviour pattern and light exposure. Also, light exposure related behaviours can be dependent upon the socio-economic status as behaviours can be modulated by available tools individual have on their disposal. Our analysis did not consider socio-economic status, as we didn't measure it. Investigating the properties of LEBA while considering different socio-economic status would be a valuable addition.

>>>>

**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.

**Lastly**, we developed a short form of LEBA using Item Response Theory (IRT) based analysis. We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`). IRT assesses the item quality by estimating item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017]. Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$). Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%. Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017]. We discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA. We also assessed the precision of the short LEBA using Test information curve (TIC). TIC indicates the amount of information a particular scale carries along the latent trait continuum. Item fit and person fit of the fitted IRT models were also analysed to gather more evidence on validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018]. Item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit. Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].

@@

### Exploratory Factor Analysis and Reliability Analysis

@@

### Confirmatory Factor Analysis

@@

png(filename="Figures/CFAplot2.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=12, 
    pointsize=12, 
    res=1200)
semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=T,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20). We discarded those items which yielded a short form of LEBA with 5 factors and 18 items.

@@

We treated each factor of short-LEBA as a unidimensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)). These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$). The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].

@@

Though there are lots of validated scale to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure. At present there is a dearth of validated scale to measure light exposure related behaviours. In that vein we have developed a subjective self-reported scale that can capture light exposure related behaviour in different dimensions.

@@

We developed a novel self-reported subjective scale-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour. We developed 48 items, judged the relevance and content of the items and conducted a large scale geographically unrestricted cross-sectional survey. Our EFA gave a five solution with 25 items. A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded. The 23-item "LEBA" was found reliable (internal consistency) and valid (structural validity). A short-form of LEBA was developed using IRT analysis. IRT analysis gave a 18-item scale with a good coverage across the underlying trait continuum. Hence, we could recommend that LEBA can be used to measure different aspects of light exposure related behaviour.

@@

Since, LEBA is the first of its kind, estimating convergent validity with other subjective scale was not possible. One way to establish the convergent validity of LEBA is to administer this subjective scale along which some objective measurement scales (e.g. personalised light dosimeter). Though such objective scales do not directly capture light exposure related behaviour, potential insight can be drawn by understanding the behaviour pattern and light exposure. Also, light exposure related behaviours can be dependent upon the socio-economic status as behaviours can be modulated by available scales individual have on their disposal. Our analysis did not consider socio-economic status, as we didn't measure it. Investigating the properties of LEBA while considering different socio-economic status would be a valuable addition.
